Weakly Nonlinear MRI: Notes

### 2014-04-07 notes/mri_notes.tex
fixed

I believe one can state this as ``$\mathbb{V}^\dagger$ must be orthogonal to $\widetilde{\mathcal{L}}_1 \mathbb{V}_{11}$". Because both $\mathbb{V}^\dagger$ and $\mathbb{V}_{11}$ are even symmetric about x = 0, the requirement is really that $\widetilde{\mathcal{L}}_1 \mathbb{V}_{11}$ is odd symmetric with respect to x, XOR $\partial_Z \alpha(T, Z)$ is odd symmetric with respect to x = 0.

>>>>

I believe one can state this as ``$\mathbb{V}^\dagger$ must be orthogonal to $\widetilde{\mathcal{L}}_1 \mathbb{V}_{11}$". Because both $\mathbb{V}^\dagger$ and $\mathbb{V}_{11}$ are even symmetric about x = 0, the requirement is really that $\widetilde{\mathcal{L}}_1 \mathbb{V}_{11}$ is odd symmetric with respect to x, since $\partial_Z \alpha(T, Z)$ is presumably not zero everywhere.
